quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-10-23 paper-quollr.Rmd
Updated Figure 2 title

```{r workflow, out.width = "100%", fig.pos="H", fig.cap="Workflow for "}

>>>>

```{r workflow, out.width = "100%", fig.pos="H", fig.cap="Overview of the `quollr` workflow and software architecture. The process begins with NLDR and $p\\text{-}D$ data inputs, followed by data preprocessing and hexagonal binning. Centroids are computed and triangulated to form the $2\\text{-}D$ mesh, which is then lifted into the $p\\text{-}D$ space. Predictions and error computations are performed on new data, while interactive functions enable dynamic linking between the $p\\text{-}D$ and $2\\text{-}D$ representations."}

### 2025-10-23 paper-quollr.tex
Added Figure 1 title
Updated Figure 2 title

\begin{figure}[H]
\includegraphics[width=1\linewidth]{figures/quollr_workflow} \caption{Workflow for }\label{fig:workflow}
\end{figure}

@@

The source code for reproducing this paper can be found at: \url{https://github.com/JayaniLakshika/paper-quollr}.

This article is created using \CRANpkg{knitr} \citep{yihui2015} and \CRANpkg{rmarkdown} \citep{yihui2018} in R with the \texttt{rjtools::rjournal\_article} template. These \texttt{R} packages were used for this work: \texttt{cli} \citep{gabor2025}, \texttt{dplyr} \citep{hadley2023}, \texttt{ggplot2} \citep{hadley2016}, \texttt{interp} (\textgreater= 1.1-6) \citep{albrecht2024}, \texttt{langevitour} \citep{paul2023}, \texttt{proxy}\citep{david2022}, \texttt{stats} \citep{core2025}, \texttt{tibble} \citep{kirill2023}, \texttt{tidyselect} \citep{lionel2024}, \texttt{crosstalk} \citep{joe2023}, \texttt{plotly} \citep{chapman2020}, \texttt{htmltools} \citep{joe2024}, \texttt{kableExtra} \citep{hao2024}, \texttt{patchwork} \citep{thomas2024}, and \texttt{readr} \citep{hadley2024}.

>>>>

\begin{figure}[H]
\includegraphics[width=1\linewidth]{figures/quollr_workflow} \caption{Overview of the `quollr` workflow and software architecture. The process begins with NLDR and $p\text{-}D$ data inputs, followed by data preprocessing and hexagonal binning. Centroids are computed and triangulated to form the $2\text{-}D$ mesh, which is then lifted into the $p\text{-}D$ space. Predictions and error computations are performed on new data, while interactive functions enable dynamic linking between the $p\text{-}D$ and $2\text{-}D$ representations.}\label{fig:workflow}
\end{figure}

@@

The source code for reproducing this paper can be found at: \url{https://github.com/JayaniLakshika/paper-quollr}. This article is created using \CRANpkg{knitr} \citep{yihui2015} and \CRANpkg{rmarkdown} \citep{yihui2018} in R with the \texttt{rjtools::rjournal\_article} template. These \texttt{R} packages were used for this work: \texttt{cli} \citep{gabor2025}, \texttt{dplyr} \citep{hadley2023}, \texttt{ggplot2} \citep{hadley2016}, \texttt{interp} (\textgreater= 1.1-6) \citep{albrecht2024}, \texttt{langevitour} \citep{paul2023}, \texttt{proxy}\citep{david2022}, \texttt{stats} \citep{core2025}, \texttt{tibble} \citep{kirill2023}, \texttt{tidyselect} \citep{lionel2024}, \texttt{crosstalk} \citep{joe2023}, \texttt{plotly} \citep{chapman2020}, \texttt{htmltools} \citep{joe2024}, \texttt{kableExtra} \citep{hao2024}, \texttt{patchwork} \citep{thomas2024}, and \texttt{readr} \citep{hadley2024}.
